Synthesising Concise Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-08 papers/termination/paper.tex
theorem 14

If this formula is satisfiable, $N$ is an open recurrence set for $L$, which proves
$L$'s non-termination. The issue with this formula is the additional level of quantifier alternation as compared to the synthesis fragment
(it is an $\exists \forall \exists$ formula).  To eliminate the innermost existential quantifier,
we introduce a Skolem function $S$, which we then existentially quantify over.  This results in
formula {\bf [SNT]} (Definition~\ref{def:snt}).

@@

\begin{theorem}
\label{thm:cnt}
 If $T$ is deterministic,
 Definition~\ref{def:ont} and Definition~\ref{def:cnt} are equisatisfiable.
\end{theorem}

>>>>

If this formula is satisfiable, $N$ is an open recurrence set for $L$, which proves
$L$'s non-termination. The issue with this formula is the additional level of quantifier alternation as compared to the synthesis fragment
(it is an $\exists \forall \exists$ formula).  To eliminate the innermost existential quantifier,
we introduce a Skolem function $C$ that chooses the successor $x'$, which we then existentially quantify over.  This results in
formula {\bf [SNT]} (Definition~\ref{def:snt}).

@@

\begin{theorem}
\label{thm:cnt}
 If $T$ is deterministic,
formula {\bf [ONT]} (Definition~\ref{def:ont}) and formula {\bf [CNT]} (Definition~\ref{def:cnt}) are equisatisfiable.
\end{theorem}
